Paper Title*\\ {\footnotesize \textsuperscript{*}Note: Sub-titles are not captured in Xplore and should not be used} \thanks{Identify applicable funding agency here. If none, delete this.}

### 2019-05-01 icdm/submission/includes/background.tex
new file for evalutation and changes to tables
layers of sgm better explained

\section{Background}\label{chap:background}

\begin{table*}[tb]\centering
    \caption{Sample Caption}
    %\scriptsize
    \begin{tabular}{l r r r r r r r}%
        \toprule
        \textbf{App} & \textbf{NSGA-II} & \textbf{Random} & \textbf{Heuristic} & \textbf{Simple {ga}} & \textbf{MOSA} & \textbf{MIO} \\%
        \midrule%
        moneywallet        & 0.20 & 0.40 & 0.40 & 0.22 & 0.22 & 0.19 \\%
        shoppinglist       & 0.77 & 0.78 & 0.84 & 0.77 & 0.77 & 0.77 \\%
        periodical         & 0.85 & 0.86 & 0.87 & 0.84 & 0.83 & 0.85 \\%
        drhoffmannsoftware & 0.44 & 0.48 & 0.45 & 0.44 & 0.46 & 0.48 \\%
        activitydiary      & 0.74 & 0.82 & 0.82 & 0.73 & 0.74 & 0.75 \\%
        bierverkostung     & 0.43 & 0.65 & 0.63 & 0.44 & 0.45 & 0.49 \\%
        easy\_xkcd         & 0.62 & 0.73 & 0.68 & 0.57 & 0.59 & 0.60 \\%
        markor             & 0.62 & 0.68 & 0.65 & 0.61 & 0.60 & 0.60 \\%
        redreader          & 0.55 & 0.61 & 0.50 & 0.52 & 0.54 & 0.52 \\%
        rentalcalc         & 0.67 & 0.77 & 0.76 & 0.68 & 0.68 & 0.71 \\%
        \midrule%
        Mean               & 0.59 & 0.68 & 0.66 & 0.58 & 0.59 & 0.60 \\%
        \bottomrule%
   \end{tabular}%
   \label{tab:sample_label}%
\end{table*}
This subsection gives an overview of the SGM and related work on its optimization. Furthermore, the used optimizers in our experiments are explained.
\subsection{The Skip-Gram Model}
The SGM is a very simple model used to learn WE. The idea is to train the model, a neural network, on a fake task and then use some of the weights of the neural network as embeddings. To understand this fake task center and context words must be defined. The center word is any given word in a sentence, from which we want to learn the WE. The context words of this specific center word are the words left and right in a given window $m$ in the sentence. See Figure \ref{fig:window_ex} as an example, where the context words are highlighted. An important thing to notice, is that instead of having a fixed window size $m$, each word will randomly have a window size between $1$ and $m$. The idea behind having different window sizes is that words that are further away in the sentence, have less semantic correlation to the center word.

\begin{figure}[h]
\centering
\includegraphics[scale=0.18]{images/window_ex}
\caption{Example of a center word and it's context words}
\label{fig:window_ex}
\end{figure}
%TODO think about example matrix
With these definitions the fake task can be defined: given a pair of center and context words, which will be our training samples, the goal of the network is to predict the probability of each word to appear in the context of the center word. One may ask how such a network is built. The network consists of two matrices, a projection and an output layer. Both of these matrices store word embeddings. The first one, the projection layer, will store the WE for one specific word in one specific row. It will have dimension $T\times d$, with $T$ being the size of our vocabulary and $d$ the dimension of our WE. The second layer, the output layer, will store one WE in each column. The idea behind these 2 layers is that the input layer will represent our words as center word and the output layer as context words. Since the task of the network being to predict the probability of each word appearing in the context of a given center word, the following probability should be maximized:\\
\begin{equation} \label{eq:basicSkip}
\prod_{t=1}^T \prod_{-m<j<m} p(w_{t+j}|w_t)
\end{equation}
Where T is the number of words in the corpus data, $w_t$ the $t^{th}$ word in the corpus data and $m$ is the context window. This means that the $m$ nearest words to $w$ are considered as context words.
Equation \ref{eq:basicSkip} can be transformed into sums by using log probabilities:
\begin{equation}
\sum _{t=1}^T \sum_{-m<j<m} log( p(w_{t+j}|w_t) )
\end{equation}
where the parameters are the same as in Equation \ref{eq:basicSkip}.

@@

Here $\tilde{v}_{w_t}$ and $ v_{w_t}$ are the vector representations, stored respectively in the projection Layer (first Matrix) and in the output layer (second Matrix). There is a problem with the classical softmax. As a matter of fact, it is unsuitable to compute the softmax. For the computation of $\sum_{w=1}^v exp(\tilde{v_w}^T w_t)$, the denominator in Equation \ref{eq:softmax}, one has to go over the whole corpus data. As very big data sets are needed to train the model, this is not a solution. Mikolov et al. \cite{mikolov2} proposed different solutions. The first solution is to use a Hierarchical softmax introduced by Morin and Bengio \cite{hsoftmax}. In this model, the probability distribution of the output nodes is saved in a binary tree which gives one a logarithmic computation time for each of these probabilities and makes it suitable to compute the softmax. Another possibility is the use of negative sampling which is discussed in the next subsection.

>>>>

\section{Background}\label{chap:background}
\iffalse
\begin{table*}[tb]\centering
    \caption{Sample Caption}
    %\scriptsize
    \begin{tabular}{l r r r r r r r}%
        \toprule
        \textbf{App} & \textbf{NSGA-II} & \textbf{Random} & \textbf{Heuristic} & \textbf{Simple {ga}} & \textbf{MOSA} & \textbf{MIO} \\%
        \midrule%
        moneywallet        & 0.20 & 0.40 & 0.40 & 0.22 & 0.22 & 0.19 \\%
        shoppinglist       & 0.77 & 0.78 & 0.84 & 0.77 & 0.77 & 0.77 \\%
        periodical         & 0.85 & 0.86 & 0.87 & 0.84 & 0.83 & 0.85 \\%
        drhoffmannsoftware & 0.44 & 0.48 & 0.45 & 0.44 & 0.46 & 0.48 \\%
        activitydiary      & 0.74 & 0.82 & 0.82 & 0.73 & 0.74 & 0.75 \\%
        bierverkostung     & 0.43 & 0.65 & 0.63 & 0.44 & 0.45 & 0.49 \\%
        easy\_xkcd         & 0.62 & 0.73 & 0.68 & 0.57 & 0.59 & 0.60 \\%
        markor             & 0.62 & 0.68 & 0.65 & 0.61 & 0.60 & 0.60 \\%
        redreader          & 0.55 & 0.61 & 0.50 & 0.52 & 0.54 & 0.52 \\%
        rentalcalc         & 0.67 & 0.77 & 0.76 & 0.68 & 0.68 & 0.71 \\%
        \midrule%
        Mean               & 0.59 & 0.68 & 0.66 & 0.58 & 0.59 & 0.60 \\%
        \bottomrule%
   \end{tabular}%
   \label{tab:sample_label}%
\end{table*}

\fi
This subsection gives an overview of the SGM and related work on its optimization. Furthermore, the used optimizers in our experiments are explained.
\subsection{The Skip-Gram Model}
The SGM is a very simple model used to learn WE. The idea is to train a neural network, on a fake task and then use some of the weights of the network as embeddings. To understand this fake task center and context words must be defined. The center word is any given word in a sentence, from which we want to learn the WE. The context words of this specific center word are the words left and right in a given window $m$ in the sentence. See Figure \ref{fig:window_ex} as an example, where the context words are highlighted. An important aspect to notice, is that instead of having a fixed window size $m$, each word will randomly have a window size between $1$ and $m$. The idea behind having different window sizes is that words that are further away in the sentence, have less semantic correlation to the center word.

\begin{figure}[h]
\centering
\includegraphics[scale=0.18]{images/window_ex}
\caption{Example of a center word and it's context words}
\label{fig:window_ex}
\end{figure}
%TODO think about example matrix
With these definitions the fake task can be defined: given a pair consisting of a center and a context words, which will be our training samples, the goal of the network is to predict the probability of each word to appear in the context of the center word. To achieve this goal, Mikolov et al. introduced the following model. The network consists of three layers. See fig x for an illustration. First the ntw has an input layer, a vector of size $V$ ( $V$ being the size of the vocabulary), represint words as an one hot encoding. Secondly, the projection layer wight Matrix $M_{in}$ soters $V$ $D$-dimensional vectors for the corresponding word in the vocabulary  in it's rows. The projection layer serves as a look up tavle for our WE (if a one hot vector is multiplied with $M_{in}$ the corresponding WE will result). Finally, the output layer wight matrix $M_{out}$ also stores $V$ $D$-dimensional vector representation of words.The idea behind these 2 Matrices is that the input layer will represent our words as center word and the output layer as context words. Since the task of the network being to predict the probability of each word appearing in the context of a given center word, the following probability should be maximized:\\
\begin{equation} \label{eq:basicSkip}
\prod_{t=1}^T \prod_{-m<j<m} p(w_{t+j}|w_t)
\end{equation}
Where T is the number of words in the corpus data, $w_t$ the $t^{th}$ word in the corpus data and $m$ is the context window. This means that the $m$ nearest words to $w$ are considered as context words.
Equation \ref{eq:basicSkip} can be transformed into sums by using log probabilities:
\begin{equation}
\sum _{t=1}^T \sum_{-m<j<m} log( p(w_{t+j}|w_t) )
\end{equation}
where the parameters are the same as in Equation \ref{eq:basicSkip}.

@@

Here $\tilde{v}_{w_t}$ and $ v_{w_t}$ are the vector representations, stored respectively in the projection Layer ($M_{in}$) and in the output layer ($M_{out}$). There is a problem with the classical softmax. As a matter of fact, it is unsuitable to compute the softmax. For the computation of $\sum_{w=1}^v exp(\tilde{v_w}^T w_t)$, the denominator in Equation \ref{eq:softmax}, one has to go over the whole corpus data. As very big data sets are needed to train the model, this is not a solution. Mikolov et al. \cite{mikolov2} proposed different solutions. The first solution is to use a Hierarchical softmax introduced by Morin and Bengio \cite{hsoftmax}. In this model, the probability distribution of the output nodes is saved in a binary tree which gives one a logarithmic computation time for each of these probabilities and makes it suitable to compute the softmax. Another possibility is the use of negative sampling which is discussed in the next subsection.
